### 2014-06-28 Choosing R3 Relations.tex
added_square_r3b

\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}

@@

\begin{document}

%This adds the list of todos to the first page.
\listoftodos
\newpage

@@

\begin{defn}
Using the notation as in Barot - Marsh, given a chordless cycle C in $\Gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
\end{defn}

@@

\begin{lem}[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
\end{lem}

@@

\begin{lem} (4.2 Analog)
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

To show the first, equivalence, note
\begin{align*}
	s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 &=
\end{align*}

@@

Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw,$ we can obtain $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$

@@

>>>>

\usepackage[all]{xy}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newcommand\fri{s_4^{-1}}
\newcommand\fr{s_4}
\newcommand\tri{s_3^{-1}}
\newcommand\tr{s_3}
\newcommand\twi{s_2^{-1}}
\newcommand\tw{s_2}
\newcommand\oni{s_1^{-1}}
\newcommand\on{s_1}

@@

\usepackage{amsmath}
\begin{document}

%This adds the list of todos to the first page.
\listoftodos
\begin{enumerate}
	\item Verify ~\ref{square_mutation_preserved}
	\item Verify that the relations (a),(b) are equivalent in ~\ref{4.2_analog} and ~\ref{4.4_analog}
	\end{enumerate}
\newpage

@@

\begin{defn}
Using the notation as in Barot - Marsh, given a chordless cycle C in $\Gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.

An equivlent relation is as follows

$s_a^{-1} s_{a+1}^{-1}\cdots s_{a-1}^{-1}s_{a-2}\cdots s_a s_{a+1}^{-1}\cdots s_{a-2}^{-1} s_{a-1}\cdots s_{a+1}$
\end{defn}

@@

\begin{lem}
\label{5.2 analog}
[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
\end{lem}

@@

\begin{lem} 
\label{4.2_analog}
(4.2 Analog)
Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
\end{lem}
\begin{proof}

@@

Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw.$
To verify this, note:
\begin{align*}
	e &= \twi\tri\oni\tr\tw\tri\on\tr \iff \\
	e &= \twi\tri\oni\tri\tw\tr\on\tr \iff \\
	e &= \tri\oni\tri\twi\tr\on\tr\tw \iff \\
	e &= \tri\twi\tr\on\tr\tw\tri\oni \iff \\
	\tw\tr &= \tr\on\tr\on\tw\tri\oni \iff \\
	 \tw\tr &= \oni\tr\on\tr\on\on\tw\tri\oni \iff \\
\end{align*} 
Where an equivalent form of $\tw\tr\tr = \tr\tr\tw.$ is used in going from the first line to the second in the above computation.

@@

\begin{prop}
\label{commuting_triples}
For the case of the (2,1,2,1) square, we have $\twi\tri\tw\fri\oni\fr = \fri\oni\fr\twi\tri\tw.$
By inverting both sides of this relation, we also obtain
$\fri\on\fr\twi\tr\tw = \tri\tr\tw\fri\on\fr.$
\end{prop}
\begin{proof}
Using the cyclic $r(1,2)$ relation we have
\begin{align*}
	e &= \oni\twi\tri\fri\tr\tw\on\twi\tri\fr\tr\tw\\
	&= \oni\twi\fr\tri\fri\tw\on\twi\fr\tr\fri\tw \\
	&= \oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw\fri \iff \\
	e &= \fri\oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw \iff \\
	\twi\tri\tw\fri\oni\fr &= \fri\oni\fr\twi\tri\tw
\end{align*}
\end{proof}

\begin{lem}
\label{4.4_analog} (Analog of 4.4) For the case of the (2,1,2,1) square, assuming the relations from ~\ref{even_more_relations} we get that the analogs of $r(1,2)^2 = e,r(3,4)^2 = e$ are equivalent, and they imply the following relation, which is an analog of R3b:

$$\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr=e.$$
\end{lem}
\begin{proof}
Hailee said she showed that the analogs of $r(1,2),r(3,4)$ are equivalent.

So, I will only show that these relations imply the analog of $R3b.$

\begin{align*}
	e &=\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr \iff
	\\
	e &= (\twi\tr\fri\on\fr\tr)(\tw\tri\fri\on\fr\tri)(\twi\tri\fri\oni\fr\tr) \iff
	\\
	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
	\\
	&= (\tr\twi\tr\fri\on\fr)(\tr\tw\tri\fri\on\fr)(\tr\twi\tri\fri\oni\fr)
\end{align*}

Now observe that $$\twi\tr\tw\tri\twi = \tr\tw\twi\twi = \tr\twi\tr,$$ by ~\ref{even_more_relations} in the second equality.
Also, $$\tw\tri\twi\tr\tw = \twi\tri\tw\tr\tw = \tr\tw\tri$$ again using ~\ref{even_more_relations} in the first equality.
And finally,
$$\twi\tri\twi\tri\tw = \tri\twi\tri.$$
So, substituting these three equations in the above, we have 
\begin{align*}
	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
	\\
	&= ((\tr\twi\tr)\fri\on\fr)((\tr\tw\tri)\fri\on\fr)((\tr\twi\tri)\fri\oni\fr)
	\\
	&=((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)
\end{align*}
Now, using ~\ref{commuting_triples} three times, we have

\begin{align*}
	&((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)\\
	&= (\twi\tr(\fri\on\fr\tw\tr\twi))(\twi\tr(\fri\on\fr\twi\tr\tw))(\twi\tri(\fri\oni\fr\twi\tri\tw))
	&=
	(\twi\tr\fri\on\tw\fr\tr\twi)(\twi\tr\fri\on\twi\fr\tr\tw)(\twi\tri\fri\oni\twi\fr\tri\tw)
	\\
	&= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw
\end{align*}

Therefore,

\begin{align*}
	e &= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw \iff \\
	e &=  \on\tw\on\twi\oni\twi
\end{align*}
Which if of course one of our basic R2 relations.
\end{proof}

\begin{thm}
\label{square_mutation_preserved}
The relations described in ~\ref{even_more_relations} are permuted (and hence preserved) after mutation at any vertex.
\end{thm}
\begin{proof}
This is what additionally needs to be checked in ~\ref{5.2 analog} by adding ~\ref{even_more_relations} in the cases corresponding to cycles with edges of weight 2 in the paper. I.e. it has to be checked in cases (b,c,d,e,f,g,h). It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out. 
\end{proof}
